Title

### 2024-05-12 paper/main.tex
udpates

\begin{abstract}
	\emph{Causal Discovery} is the process of learning the causal structure
	either in form of a Directed Acyclic Graph (DAG) or a Structural
	Equation Model (SEM) from observational data. This problem has been
	extensively studied for both DAGs and SEMs.
	In the field of DAGs, many automated algorithms
	have been developed for constructing a DAG from a given dataset. However, the
	adaption of these algorithms in applied fields have been limited,
	possibly due to a lack of confidence in these algorithms stemming from
	them making obvious mistakes, and the difficulties in choosing the
	right algorithm for a given dataset. Consequently, in applied
	disciplines, these DAGs are predominantly constructed manually based on
	domain expertise. Due to being constructed by hand, it is vital that
	the fit of these models are tested against data and the models are
	potentially modified to acheive a better fit. On the other hand, in the
	field of SEMs models are typically constructed manually through an
	iterative process of assessing fit and modifying the model according to
	that. This process is commonly known as \emph{Specification Search} 
	where things like \emph{modification indices} can be used to guide this
	modification process. In the case of DAGs, although there are tests
	such as Shipley 2000 that can assess the global fit of model by
	combining the implied conditional independencies of the model, but
	there are no methods that can guide our modification process. In this
	paper, we present a simple modification process based on using a
	measure of association for these individual local CI tests and
	combining it with expert knowledge. We also present a measure of
	association based on canonical correlations for mixed data. We also
	present a graphical web-tool that can assist researchers in iteratively
	modifying and constructing their DAGs. We theoretically show that in
	the presence of an oracle, this iterative modification process is
	consistent in recovering the true DAG. Emprically, we show that this
	process performs comparably to PC and Hill-Climb Search algorithms if
	the user is able to correctly identify the direction of the edge in one
	out of three cases.
\end{abstract}

>>>>

\begin{abstract}
	\emph{Causal Discovery} is the process of learning the causal structure
	either in form of a Directed Acyclic Graph (DAG) or a Structural
	Equation Model (SEM) from observational data. This problem has been
	extensively studied for both DAGs and SEMs.
	In the field of DAGs, many automated algorithms
	have been developed for constructing a DAG from a given dataset. However, the
	adaption of these algorithms in applied fields have been limited,
	possibly due to a lack of confidence in these algorithms stemming from
	them making obvious mistakes, and the difficulties in choosing the
	right algorithm for a given dataset. Consequently, in applied
	disciplines, these DAGs are predominantly constructed manually based on
	domain expertise. Due to being constructed by hand, it is vital that
	the fit of these models are tested against data and the models are
	potentially modified to acheive a better fit. On the other hand, in the
	field of SEMs models are typically constructed manually through an
	iterative process of assessing fit and modifying the model according to
	that. This process is commonly known as \emph{Specification Search} 
	where methods like \emph{modification indices} can be used to guide this
	modification process. In the case of DAGs, although there are tests
	such as Shipley 2000 that can assess the global fit of model by
	combining the tests using implied conditional independencies of the model, but
	there are no methods that can guide our modification process. In this
	paper, we present a simple modification process aimed at helping researchers
	in manually constructing or modifying the DAGs outputted by an algorithm.
	This modification process is based on using a measure of association for 
	these individual local CI tests to identify the worst offending CI test and
	combining it with expert knowledge. We also present a measure of
	association based on canonical correlations for mixed data. We also
	present a graphical web-tool that can assist researchers in iteratively
	modifying and constructing their DAGs. We theoretically show that in
	the presence of an oracle, this iterative modification process is
	consistent in recovering the true DAG. Emprically, we show that this
	process performs comparably to PC and Hill-Climb Search algorithms if
	the user is able to correctly identify the direction of the edge in one
	out of three cases.
\end{abstract}
